An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This work has been partially funded by CoMeDiC ANR-15-CE40-0006 research grant.}

### 2020-01-07 answer-to-reviewers/answer-to-reviewers.tex

We thank the reviewers for their time, consideration and thoughtful comments. Our article has been amended
according to their recommendations. Changes in the text are highlighted in red. In addition, our replies follow.

\section{Reviewer \#1}

\paragraph{This is an interesting contribution to digital processing of images. Alternative approaches to discretization of elastica based on polygonal approximations for discrete elastica and their convergence issues could be mentioned for comparison}

~\\
~\\
$\rightarrow$ In section 5, we indeed compare our segmentation model with the
work of \cite{schoenemann09linear}, which uses a polygonal
approximation of discrete elastica. In this work, the curvature is
estimated with a simple formula involving angle and edge lengths at
polygon vertices as proposed in \cite{bruckstein96}. This discrete
elastica problem with fixed end-points is proven to be
$\Gamma$-convergent toward the continuous elastica problem in
\cite{bruckstein01}. However it is not straightforward to include
image data term in this work, since the optimization variables of the
polygonal approximation are not related to the digital domain. For
instance, one could also use splines approximation with exact
curvature information and the same kind of approach would have the
same pros and cons.

@@

We remark that our approach never leaves the digital domain. In other
words, it is purely digital and it does not rely on any curve
representation. With this approach, all the optimization variables are
related to the digital domain, and we can thus optimize in the same
process data terms and elastica terms. Hence there is no alternate
minimization involved.

Finally, the notions of multigrid convergence and $\Gamma$-convergence
are not related. The former concerns the accuracy of an
estimation, and is specifically designed for digital data, hence more appropriated in
our case as our main objects of interest are digital images.  The latter concerns a
sequence of minimizers especially in the continuous domain.~\\

@@

\textbf{8:14--16 Probably a reference for "the cellular-grid model" may be in place.
Moreover, some short explanation would be welcom regarding the basic
components, especially "linels" and "pointels". I can guess what a linel is
but what are pointels, i.e., how do they differ from points?}

~\\
$\rightarrow$ An additional figure and further explanation was incorporated in the manuscript.
~\\

\textbf{8:42--44 I guess for gluing curves, some hypothesis on $C_1, C_2$ and/or $c_1, c_2$
is needed, so they can actually be connected by linels. This should be added.
Moreover, I understand that $c_1$ and $c_2$ are clipped from $C_1$ and $C_2$ but the
$\in$ symbol (=element of a set?!) does not express this well. $\subset$ or
$\subseteq$ would be better but would still need some constraining sentence.}

~\\
$\rightarrow$ We agree. In fact, the former presentation included unnecessary technical difficulties. We decided to change the presentation to an equivalent one, easier to read.
~\\

@@

\textbf{9:21--26 In the unnumbered displayed equation int is applied to sets of curves (according to Def. 8) but it is only explained in the text what int is for a single curve. Some explanation is needed how this transfers to sets of curves, in order for the reader to interpret the unnumbered displayed equation.}

~\\
$\rightarrow$ Indeed, an extension of the operator int(.) for set of curves was necessary. However, as said in the
previous answer, the presentation of this section has changed, and this definition is no longer needed.
~\\

@@

\textbf{Cross references are incorrect. Algorithm 1 is cited as algorithm 11 in the manuscript.
Please check latex file of your manuscript.}

~\\
$\rightarrow$ Thank you for pointing out. Corrections were made.
~\\

~\\
\textbf{Eq. (4) is proposed in this paper.
"Gradient flow" like evolution of digital planar boundary which minimises energy of eq. (4).
For the understanding of the differences and similarity between definitions for eqs. (3) and (4),
step-by-step graphical descriptions of definitions and equations in section 2 are preferable.}

~\\
$\rightarrow$ We have significantly changed, and hopefully simplified our description also taking into account the
other reviewers' comments.
~\\

### 2020-01-07 jmiv.tex
revision version

\begin{definition}[$n$-neighborhood]
\revision{
	Given a digital shape $S \in \Omega$, its $n$-neighborhood $\mathcal{N}_n(S)$ is defined as the set of digital shapes that can be built from $S$ by adding or removing a sequence of $k \in [0,n]$ connected pixels in $R_1(S)$.
}
\end{definition}

>>>>

\begin{definition}[$n$-neighborhood]
\revision{
	Given a digital shape $S \in \Omega$, its $n$-neigh\-bor\-hood $\mathcal{N}_n(S)$ is defined as the set of digital shapes that can be built from $S$ by adding or removing a sequence of $k \in [0,n]$ connected pixels in $R_1(S)$.
}
\end{definition}
